Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-03-23 FIE2019.tex
Added references to Oudshoornetal2018a (and deleted JHD's notes)

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accedited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019) \cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}

>>>>

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accedited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots.
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}
